Automated verification of stand-alone solar photovoltaic systems

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed experimental results
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The total were five case studies evaluated by HOMER Pro and by the automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shown that the restrictions were met by four systems, without any indication of sizing error or even of performance. The case study that was not successful during simulation was the 1,200 W (house 5), however without indication what are the fail of this PV system. All the simulations took less than 5 seconds (each) to be performed.

However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was not correct (the verification counterexample demands 3 panels in parallel and the sized project has 2 in series and 2 in parallel). That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). But it is understandable that this problem occurs because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house.

Related to the four 700 W PV systems, the sizing check was successful during automated verification, but there were found flaws in everyone, all related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaws right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4. This functional problem was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------

>>>>

We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four systems \textcolor{red}{which four system? can you please identify each one by a number? they should also be described}, without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.

However, related to the results of the automated verification, the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system, we identified that, in fact, the system mostly of the time does not meet the battery autonomy (mainly when all the loads are turned on). However, it is understandable that this problem occurs since the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house.

Related to the four 700 W PV systems, the sizing check was successful during automated verification, but flaws were found in all of them, all related with the battery autonomy, when SOC reached levels below 75\%. The automated verification identified the flaws right after the first night-discharge cycle, i.e., before the solar system starts recharging the batteries. The proposed method took 409.3 hours to find an error in house 1, and the maximum of \textcolor{red}{456XXX} hours to house 4. This functional problem \textcolor{red}{what is a functional problem?} was confirmed with all the four dwellers that use the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation.
%At the terminal, the command used to perform the verification is:
%\$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard --z3
%
%Where:
%
%\begin{itemize}
%\item The first three parameters, after the filename, are related to options that are usual to find bug in software, %for example, like bound check to arrays, pointer check, and division by zero, 
%but unnecessary to check at this kind of problem (if not removed, there is lost of performance during the automated verification);
%\item The parameter $unmind$ tells to ESBMC the limit to unroll the loops. This number was optimized (empirically) in order to reduce the running time and avoid to unwind unnecessarily the loops;
%\item The two parameters with $symex$ tell to ESBMC to perform an incremental SMT solving. There are other options, but this parameter is necessary because the complexity of the algorithms. The incremental SMT solving uses few RAM memory, compared with other SMT solving. 
%During empirical tests of the algorithms, the incremental solving was the only one who do not demanded 100\% the RAM memory. The use of swap-memory, i.e., the use of hard disk, reduces the performance and must be avoided;
%\item And the last parameter says to the tool that the Z3 SMT solver will be used.
%\end{itemize}
%
%\subsection{Experimental results}
%\label{sec:results}
%---------------------------------------------------
\subsection{Threats to Validity}
%---------------------------------------------------
